%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


	%---------------------------------------------------------
	\cventry
	{Nanodegree(s)} % Degree
	{\href{https://www.udacity.com/}{Udacity}} % Institution
	{Remote} % {Mountain View, USA} % Location
	{September. 2017 - May. 2018} % Date(s)
	{\textcolor{black}{Member of some of the inaugural classes of the Nanodegree Program, as curated by Udacity, in partnership with IBM Watson, Amazon Alexa, Github, AT\&T, OpenAI, \& Google.}
		\begin{cvhonors}
			\cvhonor
			{\href{https://confirm.udacity.com/HJZHVDJH}{Artificial Intelligence Nanodegree}} % Award
			{\textit{
					\href{https://github.com/Vvkmnn/sudokuAI}{sudokuAI},
					\href{https://github.com/Vvkmnn/salesmanAI}{salesmanAI},
					\href{https://github.com/Vvkmnn/nqueenAI}{nqueenAI},
					\href{https://github.com/Vvkmnn/aslAI}{aslAI},
					\href{https://github.com/Vvkmnn/pacmanAI}{pacmanAI},
					\href{https://github.com/Vvkmnn/touristAI}{touristAI},
					\href{https://github.com/Vvkmnn/faceAI}{faceAI},
					\href{https://github.com/Vvkmnn/voiceAI}{voiceAI}
				}
			} % Event
			{} % Mountain View, USA} % Location
			{Apr. 2018} % Date(s)
			\cvhonor
			{\href{https://confirm.udacity.com/GTSYRMGY}{Web Development Nanodegree}} % Award
			{ \textit{
					\href{https://github.com/Vvkmnn/linuxServer}{linuxServer}, \href{https://github.com/Vvkmnn/itemCatalog}{itemCatalog}, \href{https://github.com/Vvkmnn/logAnalysis}{logAnalysis}, \href{https://github.com/Vvkmnn/movieTrailers}{movieTrailers},
					\href{https://github.com/Vvkmnn/neighbourhoodMap}{neighbourhoodMap}
				}
			} % Event
			{} %Mountain View, USA} % Location
			{Apr. 2018} % Date(s)
			\cvhonor
			{\href{https://confirm.udacity.com/XXZTHYHT}{Deep Learning Nanodegree}} % Award
			{\textit{
					\href{https://github.com/Vvkmnn/introDL}{introDL},
					\href{https://github.com/Vvkmnn/cnnDL}{cnnDL},
					\href{https://github.com/Vvkmnn/rnnDL}{rnnDL},
					\href{https://github.com/Vvkmnn/lstmDL}{lstmDL},
					\href{https://github.com/Vvkmnn/qLearningDL}{qLearningDL},
					\href{https://github.com/Vvkmnn/ganD}{ganDL}
				}
			} % Event
			{} % Mountain View, USA} % Location
			{Sep. 2017} % Date(s)
		\end{cvhonors}
		\newline\newline\newline
	}



	%---------------------------------------------------------
	\cventry
	{B. Commerce, Double Major in Finance \& Marketing with a Minor in Economics} % Degree
	{\href{http://www.sauder.ubc.ca/}{Sauder School of Business} -\href{http://www.ubc.ca/}{ University of British Columbia}}
	{Vancouver, CA} % Location
	{September. 2010 - May. 2014} % Date(s)
	{
		\textcolor{black}{  Graduated May '14 with a double specialization and minor with emphasis on financial engineering, marketing behavior, and multi-fractal analysis.} \newline\newline\newline
	}

	%---------------------------------------------------------
\end{cventries}
